---
title: "Marriage Licence Statistics Analysis"
author: 
  - Yizhe Chen
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This document analyzes marriage licence statistics in Toronto using simulated and real data."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = date, y =marriage_licenses)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "date",
       y = "marriage_licenses")
```

From 2011 to around 2019, the number of licenses remained relatively stable, with monthly counts typically ranging between 500 and 1000. However, starting in 2020, there is a notable decline in the number of licenses issued. Following this decline, the number of licenses rapidly increased, peaking at over 1500 licenses in some months.



# References

R and opendatatoronto
